*Supplementary Material*

### 2022-02-18 ms/manuscript.Rmd
Add nonmono gen table

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		sanger_sampling,
		coverage_by_rank,
		total_coverage,
		bb_coverage_by_rank,
		bb_total_coverage,
		gb_species_by_year,
		ref_files,
		other_dates,
		crown_ages,
		fossil_ferns_raw,
		family_stem_ages,
		fern_monophy_summ_tbl
	),
	store = here::here("_targets")
)
```

@@

fern_monophy_summ <-
fern_monophy_summ_tbl %>%
	mutate(
		n = as.integer(n),
		p = percent(percent)
	) %>%
	split(.$tax_level) %>%
	map(~split(., .$monophyly))
```

@@

All sampled orders, suborders, families, and subfamilies were recovered as monophyletic (or monotypic) with the exception of Polypodioideae, which is known to be paraphyletic relative to Grammitidoideae [@PteridophytePhylogenyGroupI2016].
`r fern_monophy_summ$genus$No$n` genera (`r fern_monophy_summ$genus$No$p`) were non-monophyletic (`r s_table("monophy")`).

>>>>

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		sanger_sampling,
		coverage_by_rank,
		total_coverage,
		bb_coverage_by_rank,
		bb_total_coverage,
		gb_species_by_year,
		ref_files,
		other_dates,
		crown_ages,
		fossil_ferns_raw,
		family_stem_ages,
		fern_monophy_summ_tbl,
		fern_nonmono_gen
	),
	store = here::here("_targets")
)
```

@@

# Format monophyly status as list for MS
fern_monophy_summ <-
fern_monophy_summ_tbl %>%
	mutate(
		n = as.integer(n),
		p = percent(percent)
	) %>%
	split(.$tax_level) %>%
	map(~split(., .$monophyly))

top_nonmono_subfam <-
fern_nonmono_gen %>%
	group_by(family, subfamily) %>%
	summarize(n = n(), .groups = "drop") %>%
	slice_max(n = 3, order_by = n) %>%
	assert(not_na, family, subfamily) %>%
	mutate(subfamily = fct_reorder(subfamily, n)) %>%
	mutate(n = jntools::english2(n)) %>%
	arrange(desc(subfamily))

# Double check that non-monophyletic genera outside of
# top three non-monophyletic subfamilies all have less
# than four genera each
fern_nonmono_gen %>%
	anti_join(
		top_nonmono_subfam,
		by = c("family", "subfamily")) %>%
	count(family, subfamily) %>%
	verify(
		all(n < 4), 
		error_fun = error_msg(
			"Other subfamilies besides top three don't have less than four genera each"),
		success_fun = success_logical)
```

@@

All sampled orders, suborders, families, and subfamilies were recovered as monophyletic (or monotypic) with the exception of Polypodioideae, which is known to be paraphyletic relative to Grammitidoideae [@PteridophytePhylogenyGroupI2016].
`r fern_monophy_summ$genus$No$n` genera (`r fern_monophy_summ$genus$No$p`) were non-monophyletic (`r s_table("monophy")`).
The subfamilies with the most non-monophyletic genera were `r top_nonmono_subfam$subfamily[[1]]` (`r top_nonmono_subfam$n[[1]]`), `r top_nonmono_subfam$subfamily[[2]]` (`r top_nonmono_subfam$n[[2]]`), and `r top_nonmono_subfam$subfamily[[3]]` (`r top_nonmono_subfam$n[[3]]`); other (sub)families each had four or fewer non-monophyletic genera (`r s_table("nonmono_gen")`).

### 2022-02-18 ms/si.Rmd
Add nonmono gen table

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		gb_species_by_year,
		ref_files,
		other_dates,
		du_dates_all,
		family_stem_ages,
		fossil_ferns_raw,
		pteridocat_ppgi_diff_refs_out,
		pteridocat_ppgi_diff_notes,
		fern_monophy_summ_tbl
	),
	store = here::here("_targets")
)
```

@@

```{r fossils-save, eval = params$doc_type == "doc"}
# Save if rendering to doc
write_csv(fossils_table, result_file(s_table("fossils"), "csv"))
```

@@

@@

<!-- Run the plot prep code -->
```{r, plot-prep-main}
```

>>>>

# Targets from MS workflow
tar_load(
	c(
		accepted_species,
		gb_species_by_year,
		ref_files,
		other_dates,
		du_dates_all,
		family_stem_ages,
		fossil_ferns_raw,
		pteridocat_ppgi_diff_refs_out,
		pteridocat_ppgi_diff_notes,
		fern_monophy_summ_tbl,
		fern_nonmono_gen
	),
	store = here::here("_targets")
)
```

@@

```{r fossils-save, eval = params$doc_type == "doc"}
write_csv(fossils_table, result_file(s_table("fossils"), "csv"))
```

@@

```{r nonmono-gen, eval = params$doc_type == "doc"}
fern_nonmono_gen %>%
	arrange(family, subfamily, genus) %>%
	write_csv(result_file(s_table("nonmono_gen"), "csv"))
```

**`r s_table("nonmono_gen")`**.
Non-monophyletic fern genera in FTOL (`r result_file(s_table("nonmono_gen"), "csv") %>% fs::path_file()`).
"number_tips" is the number of tips (species) in the genus.
"delta_tips" is the number of tips that do not belong to the genus but are included in the clade descending from the most common recent ancestor of the genus.
"number_intruders" is the number of intruding taxa into the genus.
"number_outliers" is the number of tips (species) belonging to the genus that appear in other clades.
Status of intruders and outliers was determined using the default cutoff level (0.5) in the R package "MonoPhy" [@Schwery2016].

@@

<!-- Run the plot prep code -->
```{r plot-prep-main}
```
